Music Perception 2: Analysis

### 2021-07-05 analysis/analysis.Rmd
add shapiro.wilk() for normality check
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## All ()
```{r ioi-all, echo = FALSE}
rating <- all # rating data

@@

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation ()
```{r, echo = FALSE}
cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
```

## Dynamics ()
```{r, echo = FALSE}
cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)
```

@@

## All ()
```{r ioi-tra-all, echo = FALSE}
ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]

@@

## Articulation ()
```{r, echo = FALSE}
cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)
```

## Dynamics ()
```{r, echo = FALSE}
cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
```

@@

## All ()
```{r cv, echo = FALSE}
cv <- dt_ioi[Subcomponent != "NA", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation ()
```{r, echo = FALSE}
cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)
```

## Dynamics ()
```{r, echo = FALSE}
cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Legato ()
```{r, echo = FALSE}
cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
```

## Staccato ()
```{r, echo = FALSE}
cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
```

## Forte ()
```{r, echo = FALSE}
cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)
```

## Piano ()
```{r, echo = FALSE}
cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)
```

@@

## Forte ()
```{r, echo = FALSE}
cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)
```

## Piano ()
```{r, echo = FALSE}
cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)
```
## Legato ()
```{r, echo = FALSE}
cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
```

## Staccato ()
```{r, echo = FALSE}
cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
```

@@

## Forte to Piano ()
```{r, echo = FALSE}
cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)
```

## Piano to Forte ()
```{r, echo = FALSE}
cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)
```
## Legato to Staccato ()
```{r, echo = FALSE}
cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
```

## Staccato to Legato ()
```{r, echo = FALSE}
cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
```

>>>>

## All
```{r ioi-all, echo = FALSE}
rating <- all # rating data

@@

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation ()
```{r, echo = FALSE}
# normality check
shapiro.test(ioi[Skill == "articulation"]$Teaching)
shapiro.test(ioi[Skill == "articulation"]$Mean)

cor.test(ioi[Skill == "articulation"]$Teaching, ioi[Skill == "articulation"]$Mean)
```

## Dynamics ()
```{r, echo = FALSE}
# normality check
shapiro.test(ioi[Skill == "dynamics"]$Teaching)
shapiro.test(ioi[Skill == "dynamics"]$Mean)

cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean)

cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
```

@@

## All
```{r ioi-tra-all, echo = FALSE}
ioi_tra <- dt_ioi[Subcomponent == "LtoS" | Subcomponent == "StoL" | Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile, Skill)]

@@

## Articulation ()
```{r, echo = FALSE}
# normality check
shapiro.test(ioi_tra[Skill == "articulation"]$Teaching)
shapiro.test(ioi_tra[Skill == "articulation"]$Mean)

cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean)

cor.test(ioi_tra[Skill == "articulation"]$Teaching, ioi_tra[Skill == "articulation"]$Mean, method = "spearman", exact = FALSE)
```

## Dynamics ()
```{r, echo = FALSE}
# normality check
shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)

cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
```

@@

## All
```{r cv, echo = FALSE}
cv <- dt_ioi[Subcomponent != "NA", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile, Skill)]

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation ()
```{r, echo = FALSE}
# normality check
shapiro.test(cv[Skill == "articulation"]$Teaching)
shapiro.test(cv[Skill == "articulation"]$CV)

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV)

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
```

## Dynamics ()
```{r, echo = FALSE}
# normality check
shapiro.test(cv[Skill == "dynamics"]$Teaching)
shapiro.test(cv[Skill == "dynamics"]$CV)

cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV)

cor.test(cv[Skill == "dynamics"]$Teaching, cv[Skill == "dynamics"]$CV, method = "spearman", exact = FALSE)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Legato ()
```{r, echo = FALSE}
# normality check
shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

cor.test(kot_all[Subcomponent == "Legato"]$Teaching, kot_all[Subcomponent == "Legato"]$Mean)
```

## Staccato ()
```{r, echo = FALSE}
# normality check
shapiro.test(kot_all[Subcomponent == "Staccato"]$Teaching)
shapiro.test(kot_all[Subcomponent == "Staccato"]$Mean)

cor.test(kot_all[Subcomponent == "Staccato"]$Teaching, kot_all[Subcomponent == "Staccato"]$Mean)
```

## Forte ()
```{r, echo = FALSE}
# normality check
shapiro.test(kot_all[Subcomponent == "Forte"]$Teaching)
shapiro.test(kot_all[Subcomponent == "Forte"]$Mean)

cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean)

cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
```

## Piano ()
```{r, echo = FALSE}
# normality check
shapiro.test(kot_all[Subcomponent == "Piano"]$Teaching)
shapiro.test(kot_all[Subcomponent == "Piano"]$Mean)

cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean)

cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
```

@@

## Forte ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean)

cor.test(vel_all[Subcomponent == "Forte"]$Teaching, vel_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
```

## Piano ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean)

cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
```
## Legato ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean)
```

## Staccato ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_all[Subcomponent == "Staccato"]$Teaching)
shapiro.test(vel_all[Subcomponent == "Staccato"]$Mean)

cor.test(vel_all[Subcomponent == "Staccato"]$Teaching, vel_all[Subcomponent == "Staccato"]$Mean)
```

@@

## Forte to Piano ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "FtoP"]$Mean)

cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean)

cor.test(vel_diff_all[Subcomponent == "FtoP"]$Teaching, vel_diff_all[Subcomponent == "FtoP"]$Mean, method = "spearman", exact = FALSE)
```

## Piano to Forte ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "PtoF"]$Mean)

cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean)

cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
```
## Legato to Staccato ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean)
```

## Staccato to Legato ()
```{r, echo = FALSE}
# normality check
shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "StoL"]$Mean)

cor.test(vel_diff_all[Subcomponent == "StoL"]$Teaching, vel_diff_all[Subcomponent == "StoL"]$Mean)
```
